---
title: "FIF Data Packages"
author: "Matt Norris"
date: "10 August 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(plyr)
library(dplyr)
library(tidyverse)
library(readxl)
library(stringr)
library(pixiedust)
library(broom)
library(RColorBrewer)
library(oce)
library(gridExtra)
library(cowplot)
library(reshape)
library(scales)
library(writexl)

```

### Data Package overview:
This code extracts data from the fluxmeter network for submission to MFE in the required 'data package' format.
Raw data frames are listed as follows:
Site_x.1 - Climate data from SWB climate Tab. Includes crop info.
Site_x.2 - Soil moisture and temperature monitoring data from the 'gold sites'
Site_x.3 - Modelled drainage at 120 cm from the SWB 'SWB' tab.
Site_x.4 - Collected drainage, nutrient concentration and nutrient loss data
Site_x.5 - Soil nutrients from "Diary and results files - soil chemical" tab. Includes mineral N, AMN, tot C, tot N, pH and OP
Site_x.6 - Crop harvest info from "Diary and results files - Biomass Summary" tab

### Set Dates
```{r, echo=FALSE} 
Date_start <- "2014-08-31"
Date_End <- "2020-08-31"
```

## Site_x.1 Function for climate data
```{r, echo=FALSE} 

Sum_x.1 <- function(x){
  x <- select(x,c("Date",Crop = "Crop_R", "Rain (mm)", "Irrigation (mm)", "Tmean (C)", "Tmin (C)", "T max(C)", "VapPress (hPa)", "Pmsl (hPa)", "Rad (MJ/m2)","WindRun (m/s)")) %>%
    mutate(Date = as.Date(Date)) %>%
    filter(Date > Date_start & Date < Date_End)
   
}

```

## Site_x.2 Function for soil moisture data
```{r, echo=FALSE} 
Sum_x.2 <- function(x){
  x <- select(x,c("Date","Average 0-30 (mm)", "Average 30-60 (mm)", "Average 60-90 (mm)", "10 cm Soil Temp (C )")) %>%
    mutate(Date = as.Date(Date))%>%
    filter(Date > Date_start & Date < Date_End)
  x
  
  x <- ddply(x, c("`Date`"), summarise,
               "SWC 0-30 cm (mm)" = mean(`Average 0-30 (mm)`),
               "SWC 30-60 cm (mm)" = mean(`Average 30-60 (mm)`),
               "SWC 60-90 cm (mm)" = mean(`Average 60-90 (mm)`),
               "10 cm soil temp (C)" = mean(`10 cm Soil Temp (C )`)) 
             
             x 
  
}
```

## Site_x.3 Function for modelled drainage
```{r, echo=FALSE}
Sum_x.3 <- function(x){
  x <- select(x, Date = col1 , Drainage = col30) %>%
    mutate(Date = as.Date(Date)) %>%
    filter(Date > Date_start & Date < Date_End)
  x
  
  x <-   rename(x, c("Drainage"="Modelled drainage at 120 cm"))
  
}


```
 


### Site_x.4 Functions are for Drainage and Nutrient Loss
###  NB: P Data is taken from an output file from P analysis code in: \\Hawdfs41\data\Common\EXPTS\Commercial\F A R\SFF Fluxmeter\Sites and Results\Fluxmeter R\Phosphorus data analysis NB: P DATE NEEDS TO BE UPDATED/REVIEWED BEFORE BEING INCLUDED IN FINAL FIF PACKAGE

## - > Sum_x.4_Gen -> Pull out drainage and nutrient data, select date range and filter outliers (SITES 1 - 7 where outlier == x and xx)
## - > Sum_x.4_S9 -> Pull out drainage and nutrient data, select date range and filter outliers (SITES 9 where outlier == xxx)
## - > Sum_x.4_S10 -> Pull out drainage and nutrient data, select date range and filter outliers (SITES 10 where outlier == xx and xxx)
## - > Sum_x.4_S11 -> Pull out drainage and nutrient data, select date range and filter outliers (SITES 11 where outlier == xx)
## - > Sum_x.4_S12 -> Pull out drainage and nutrient data, select date range and filter outliers (SITES 11 where outlier == x)

### ------- NOTE: "OUTLIER 2' IN THE SWB FILE MUST BE DENOTED 'M' WHEN MODELLED DATA IS USED TO CALCULATE LOSSES -------


## - > Sum_x.4.1 -> Select and summarise drainage data
## - > Sum_x.4.2 -> Select nutrient concentration data, remove na values and replace 'less than (<) values), Summarise nutrient concentration data into count, mean and STDEV
## - >  Sum_x.4.3 -> Select and summarise nutrient loss data

## Sum_x.4_Gen for sites 1-7
### Note = 1 means drainage data used to calculate losses, Note = 10 means modelled drainage used to calculate losses
```{r, echo=FALSE} 
Sum_x.4_Gen <- function(x){
  x <- select(x, Date = "Sampling Date" , "Outlier","Outlier 2", Drainage = "Measured Drainage (mm)", Modelled_Drainage = "Period drainage modelled (mm)",  Nitrate = "Nitrate-N (mg/L)", Ammonium = "Ammoniacal-N (mg/L)", Inorganic_N = "Inorganic-N (mg/L)", Nitrate_loss = "Nitrate-N loss (kg/ha)", Ammonium_loss = "Ammonium-N loss (kg/ha)", Inorganic_N_Loss = "Inorganic N Loss (kg/ha)") %>%
    mutate(Date = as.Date(Date)) %>%
    mutate(Note = ifelse(`Outlier 2` == "M",10,1)) %>% 
    filter(Date > Date_start & Date < Date_End) %>%
    filter(!Outlier=="x", !Outlier=="xx")
  x
}
```



## Sum_x.4_S9
### Note = 1 means drainage data used to calculate losses, Note = 10 means modelled drainage used to calculate losses
```{r, echo=FALSE} 
Sum_x.4_S9 <- function(x){
  x <- select(x, Date = "Sampling Date" , "Outlier", "Outlier 2", Drainage = "Measured Drainage (mm)", Modelled_Drainage = "Period drainage modelled (mm)",  Nitrate = "Nitrate-N (mg/L)", Ammonium = "Ammoniacal-N (mg/L)", Inorganic_N = "Inorganic-N (mg/L)", Nitrate_loss = "Nitrate-N loss (kg/ha)", Ammonium_loss = "Ammonium-N loss (kg/ha)", Inorganic_N_Loss = "Inorganic N Loss (kg/ha)") %>%
    mutate(Date = as.Date(Date)) %>%
    mutate(Note = ifelse(`Outlier 2` == "M",10,1)) %>%
    filter(Date > Date_start & Date < Date_End) %>%
    filter(!Outlier=="xxx")
  x
}
```

## Sum_x.4_S10
### Note = 1 means drainage data used to calculate losses, Note = 10 means modelled drainage used to calculate losses
```{r, echo=FALSE} 
Sum_x.4_S10 <- function(x){
  x <- select(x, Date = "Sampling Date" , "Outlier", "Outlier 2", Drainage = "Measured Drainage (mm)", Modelled_Drainage = "Period drainage modelled (mm)",  Nitrate = "Nitrate-N (mg/L)", Ammonium = "Ammoniacal-N (mg/L)", Inorganic_N = "Inorganic-N (mg/L)", Nitrate_loss = "Nitrate-N loss (kg/ha)", Ammonium_loss = "Ammonium-N loss (kg/ha)", Inorganic_N_Loss = "Inorganic N Loss (kg/ha)") %>%
    mutate(Date = as.Date(Date)) %>%
    mutate(Note = ifelse(`Outlier 2` == "M",10,1)) %>% 
    filter(Date > Date_start & Date < Date_End) %>%
    filter(!Outlier=="xx", !Outlier=="xxx")
  x
}
```


## Sum_x.4_S11
### Note = 1 means drainage data used to calculate losses, Note = 10 means modelled drainage used to calculate losses
```{r, echo=FALSE} 
Sum_x.4_S11 <- function(x){
  x <- select(x, Date = "Sampling Date" , "Outlier", "Outlier 2", Drainage = "Measured Drainage (mm)", Modelled_Drainage = "Period drainage modelled (mm)",  Nitrate = "Nitrate-N (mg/L)", Ammonium = "Ammoniacal-N (mg/L)", Inorganic_N = "Inorganic-N (mg/L)", Nitrate_loss = "Nitrate-N loss (kg/ha)", Ammonium_loss = "Ammonium-N loss (kg/ha)", Inorganic_N_Loss = "Inorganic N Loss (kg/ha)") %>%
    mutate(Date = as.Date(Date)) %>%
    mutate(Note = ifelse(`Outlier 2` == "M",10,1)) %>% 
    filter(Date > Date_start & Date < Date_End) %>%
    filter(!Outlier=="xx")
  x
}

```

## Sum_x.4_S12
### Note = 1 means drainage data used to calculate losses, Note = 10 means modelled drainage used to calculate losses
```{r, echo=FALSE} 
Sum_x.4_S12 <- function(x){
  x <- select(x, Date = "Sampling Date" , "Outlier", "Outlier 2", Drainage = "Measured Drainage (mm)", Modelled_Drainage = "Period drainage modelled (mm)",  Nitrate = "Nitrate-N (mg/L)", Ammonium = "Ammoniacal-N (mg/L)", Inorganic_N = "Inorganic-N (mg/L)", Nitrate_loss = "Nitrate-N loss (kg/ha)", Ammonium_loss = "Ammonium-N loss (kg/ha)", Inorganic_N_Loss = "Inorganic N Loss (kg/ha)") %>%
    mutate(Date = as.Date(Date)) %>%
    mutate(Note = ifelse(`Outlier 2` == "M",10,1)) %>% 
    filter(Date > Date_start & Date < Date_End) %>%
    filter(!Outlier=="x")
  x
}
```


## x.4.1
### Numeric 1 = drainage data used to calculate losses, Numeric 2 = modelled drainage used to calculate losses
```{r, echo=FALSE} 
Sum_x.4.1 <- function(x){
   x <- select(x, Date, Drainage, Note)
  
   x <- ddply(x, c("`Date`"), summarise,
               "Collected drainage (mm)" = mean(`Drainage`),
               "Sample count (includes zero volumes)"    = length(`Drainage`),
               "Collected drainage (SD)" = sd(`Drainage`),
               "Model ID"  = mean(Note))         %>%
    filter(Date > Date_start & Date < Date_End)
             
   x <-  mutate(x,"Drainage Note" = ifelse(`Model ID` == 10, "Measured drainage HIGH - Nutrient losses estimated using modelled drainage and measured conentrations","NA")) 
   
   x <- select(x, "Date", "Collected drainage (mm)", "Sample count (includes zero volumes)", "Collected drainage (SD)","Drainage Note")
   
    x
    
}

```


## x.4.2
```{r, echo=FALSE} 
Sum_x.4.2 <- function(x){
  x <- select(x, Date,  Nitrate, Ammonium, Inorganic_N) %>%
    na.omit() %>%
    mutate(Ammonium = ifelse(Ammonium =="<0.02","0.01",Ammonium)) 
    
    x$Ammonium <- as.numeric(as.character(x$Ammonium))
  
  x <- ddply(x, c("`Date`"), summarise,
               "Count [N]"    = length(`Nitrate`),
               "Nitrate-N (mg/L)" = mean(`Nitrate`),
               "Nitrate-N SD (mg/L)" = sd(`Nitrate`),
               "Ammonium (mg/L)" = mean(`Ammonium`),
               "Ammonium SD (mg/L)" = sd(`Ammonium`),
               "Inorganic-N (mg/L)" = mean(`Inorganic_N`),
               "Inorganic-N SD (mg/L)" = sd(`Inorganic_N`)) %>%
    filter(Date > Date_start & Date < Date_End)
    
    x
}

 

```
## x.4.3
```{r, echo=FALSE} 
Sum_x.4.3 <- function(x){
  x <- select(x, Date,  Nitrate_loss, Ammonium_loss, Inorganic_N_Loss)  
    
   x <- ddply(x, c("`Date`"), summarise,
               "Nitrate-N loss (kg/ha)" = mean(`Nitrate_loss`),
               "Nitrate-N loss SD (kg/ha)" = sd(`Nitrate_loss`),
               "Ammonium loss (kg/ha)" = mean(`Ammonium_loss`),
               "Ammonium SD (kg/ha)" = sd(`Ammonium_loss`),
               "Inorganic-N (kg/ha)" = mean(`Inorganic_N_Loss`),
               "Inorganic-N SD (kg/ha)" = sd(`Inorganic_N_Loss`)) %>%
    filter(Date > Date_start & Date < Date_End)
    
    x
}

 

```

### Sum_x.5 -> Soil data
```{r, echo=FALSE} 
Sum_x.5 <- function(x){
  x <- select(x,c("Date", "Rep", "Depth", "AMN", "Mineral-N", "Tot N","Tot C","pH","Olsen P")) %>%
    filter(!is.na(`Mineral-N`)) %>% 
    mutate(Date = as.Date(Date)) %>% 
        group_by(`Date`,`Rep`) %>%
     mutate_all(funs(replace(., is.na(.), ""))) %>%
    filter(Date > Date_start & Date < Date_End)
  x
  
  x$AMN <- as.numeric(as.character(x$AMN))
  x$"Mineral-N" <- as.numeric(as.character(x$"Mineral-N"))
  x$"Tot N" <- as.numeric(as.character(x$"Tot N"))
  x$"Tot C" <- as.numeric(as.character(x$"Tot C"))
  x$pH <- as.numeric(as.character(x$pH))
  x$"Olsen P" <- as.numeric(as.character(x$"Olsen P"))
  
  x <- ddply(x, c("Date", "Depth"), summarise,
        AMN = mean(`AMN`),
        "Mineral-N" = mean(`Mineral-N`),
        "Tot N" = mean(`Tot N`),
        "Tot C" = mean(`Tot C`),
        pH = mean(`pH`),
        "Olsen P" = mean(`Olsen P`))
  x
  
  x <-  reshape(x, idvar = "Date", timevar = "Depth", direction = "wide")
  
  x <-  select (x, -c("AMN.40-60","AMN.60-80","AMN.80-100", "pH.20-40", "pH.40-60", "pH.60-80", "pH.80-100","Olsen P.20-40","Olsen P.40-60", "Olsen P.60-80" ,"Olsen P.80-100" )) 

  x <-   rename(x, c("AMN.0-20"="AMN kg/ha (0-20 cm)", "AMN.20-40"="AMN kg/ha (20-40 cm)", "Mineral-N.0-20"="Min-N kg/ha (0-20 cm)", "Mineral-N.20-40"="Min-N kg/ha (20-40 cm)", "Mineral-N.40-60"="Min-N kg/ha (40-60 cm)", "Mineral-N.60-80"="Min-N kg/ha (60-80 cm)", "Mineral-N.80-100"="Min-N kg/ha (80-100 cm)", "Tot C.0-20"="Tot C % (0-20 cm)", "Tot C.20-40"="Tot C % (20-40 cm)", "Tot C.40-60"="Tot C % (40-60 cm)", "Tot C.60-80"="Tot C % (60-80 cm)", "Tot C.80-100"="Tot C % (80-100 cm)", "Tot N.0-20"="Tot N % (0-20 cm)", "Tot N.20-40"="Tot N % (20-40 cm)", "Tot N.40-60"="Tot N % (40-60 cm)", "Tot N.60-80"="Tot N % (60-80 cm)", "Tot N.80-100"="Tot N % (80-100 cm)", "pH.0-20" = "pH (0-20 cm)", "Olsen P.0-20" = "Olsen P (0-20 cm)"))

  x <- x[,c("Date","Min-N kg/ha (0-20 cm)", "Min-N kg/ha (20-40 cm)", "Min-N kg/ha (40-60 cm)", "Min-N kg/ha (60-80 cm)", "Min-N kg/ha (80-100 cm)","AMN kg/ha (0-20 cm)", "AMN kg/ha (20-40 cm)", "Tot C % (0-20 cm)", "Tot C % (20-40 cm)", "Tot C % (40-60 cm)", "Tot C % (60-80 cm)", "Tot C % (80-100 cm)", "Tot N % (0-20 cm)", "Tot N % (20-40 cm)", "Tot N % (40-60 cm)", "Tot N % (60-80 cm)", "Tot N % (80-100 cm)", "pH (0-20 cm)","Olsen P (0-20 cm)")] 
  
}


```

## Site_x.6 Function for biomass data
```{r, echo=FALSE} 

Sum_x.6 <- function(x){
  x <- select(x,c("Harvest date","Harvest number", "Whole crop yield (t DM/ha)", "Whole crop N uptake (kg N/ha)", "Whole crop P Uptake (kg P/ha)", "Marketable yield (t DM/ha)", "Marketable N uptake (kg N/ha)", "Marketable P Uptake (kg P/ha)", "Crop Notes")) 
   
  x
  
x <-   rename(x, c("Harvest date"="Date")) %>%
    mutate(Date = as.Date(Date)) %>%
    filter(Date > Date_start & Date < Date_End) 
 
}

```


### Phosphorus Data ---> This is from the P Data Analysis Code (\\Hawdfs41\data\Common\EXPTS\Commercial\F A R\SFF Fluxmeter\Sites and Results\Fluxmeter R\Phosphorus data analysis) NB: P DATE NEEDS TO BE UPDATED/REVIEWED BEFORE BEING INCLUDED IN FINAL FIF PACKAGE
```{r, echo=FALSE}

P_Data <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/FIF Data Packages/FIF Data Packages/R Files/FIF_P_DATA.xlsx", skip = 0,col_names = T)  %>%   select("Date", "Site", "Count [P]" = "n_DRP", "DRP (mg/L)" = "DRP_Conc","DRP SD (mg/L)" = "SD_DRP_Conc", "Total-P (mg/L)" = "TotP_Conc", "Total-P SD (mg/L)" = "SD_TotP_Conc", "DRP (kg/ha)"="DRP_Flux", "DRP SD (kg/ha)" = "DRP_SD",  "Total-P (kg/ha)" = "TotP_Flux", "Total-P SD (kg/ha)" = "TotP_SD") %>% 
                        mutate(Date = as.Date(Date)) %>% 
                        mutate(`DRP SD (mg/L)` = ifelse(`Count [P]` == 1, NA,`DRP SD (mg/L)`)) %>% 
                        mutate(`Total-P SD (mg/L)` = ifelse(`Count [P]` == 1, NA,`Total-P SD (mg/L)`)) %>% 
                        mutate(`DRP (kg/ha)` = ifelse(`Count [P]` == 1, NA,`DRP (kg/ha)`)) %>% 
                        mutate(`Total-P SD (kg/ha)` = ifelse(`Count [P]` == 1, NA,`Total-P SD (kg/ha)`))
```


### Site 1 Files (No 1.2 as no logging gear at this site)
```{r, echo=FALSE} 
S1.1 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Canterbury/Soil Water Balance Files/Cant Site 1 SWB (V1).xlsx",sheet = "Climate file", skip = 3,col_names = T)

S1.3 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Canterbury/Soil Water Balance Files/Cant Site 1 SWB (V1).xlsx",sheet = "soil water balance", skip = 23,col_names = paste0("col",1:63)) 

S1.4 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Canterbury/Soil Water Balance Files/Cant Site 1 SWB (V1).xlsx",sheet = "DFM data", skip = 5,col_names = T)

S1.4.1 <- P_Data %>% filter(Site == 1) %>%  select(-c("Site"))

S1.5 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Canterbury/Cant Site 1 (Mackenzie)/Results/Cant 1 Diary and Results.xlsx",sheet = "Soil Chemical", skip = 2,col_names = T)

S1.6 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Canterbury/Cant Site 1 (Mackenzie)/Results/Cant 1 Diary and Results.xlsx",sheet = "Biomass Summary", skip = 0,col_names = T)

Site1.1 <-   Sum_x.1(S1.1)
Site1.3 <-   Sum_x.3(S1.3)
Site1.4.1 <- Sum_x.4_Gen(S1.4)
Site1.4.2 <- Sum_x.4.1(Site1.4.1)
Site1.4.3 <- Sum_x.4.2(Site1.4.1)
Site1.4.4 <- Sum_x.4.3(Site1.4.1)
Site1.4.5 <- merge(Site1.4.4,S1.4.1, by = c("Date"), all = TRUE)
Site1.5.1 <- Sum_x.5(S1.5)
Site1.6 <- Sum_x.6(S1.6)

S1 <- Reduce(function(x, y) merge(x, y, all = TRUE), list(Site1.1,Site1.3,Site1.4.2, Site1.4.3, Site1.4.5, Site1.5.1, Site1.6))

write_xlsx(S1, "//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/FIF Data Packages/FIF Data Packages/Excel Data Files/Canterbury Site 1.xlsx")
  
```


### Site 2 Files (No x.2 as no logging gear at this site)
```{r, echo=FALSE} 
S2.1 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Canterbury/Soil Water Balance Files/Cant Site 2 SWB (V1).xlsx",sheet = "Climate file", skip = 3,col_names = T)

S2.3 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Canterbury/Soil Water Balance Files/Cant Site 2 SWB (V1).xlsx",sheet = "soil water balance", skip = 23,col_names = paste0("col",1:63)) 

S2.4 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Canterbury/Soil Water Balance Files/Cant Site 2 SWB (V1).xlsx",sheet = "DFM data", skip = 5,col_names = T)

S2.4.1 <- P_Data %>% filter(Site == 2) %>%  select(-c("Site"))

S2.5 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Canterbury/Cant Site 2 (Clemens)/Results/Cant 2 Diary and Results.xlsx",sheet = "Soil Chemical", skip = 2,col_names = T)

S2.6 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Canterbury/Cant Site 2 (Clemens)/Results/Cant 2 Diary and Results.xlsx",sheet = "Biomass Summary", skip = 0,col_names = T)

Site2.1 <-   Sum_x.1(S2.1)
Site2.3 <-   Sum_x.3(S2.3)
Site2.4.1 <- Sum_x.4_Gen(S2.4)
Site2.4.2 <- Sum_x.4.1(Site2.4.1)
Site2.4.3 <- Sum_x.4.2(Site2.4.1)
Site2.4.4 <- Sum_x.4.3(Site2.4.1)
Site2.4.5 <- merge(Site2.4.4,S2.4.1, by = c("Date"), all = TRUE)
Site2.5.1 <- Sum_x.5(S2.5)
Site2.6 <- Sum_x.6(S2.6)

S2 <- Reduce(function(x, y) merge(x, y, all = TRUE), list(Site2.1,Site2.3,Site2.4.2, Site2.4.3, Site2.4.5, Site2.5.1, Site2.6))

write_xlsx(S2, "//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/FIF Data Packages/FIF Data Packages/Excel Data Files/Canterbury Site 2.xlsx")
  
```


### Site 3 Files (includes measured soil moisture data)
```{r, echo=FALSE} 
S3.1 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Canterbury/Soil Water Balance Files/Cant Site 3 SWB (V1).xlsx",sheet = "Climate file", skip = 3,col_names = T)

S3.2 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Canterbury/Cant Site 3 (McEvedy)/Results/Met station/Cant 3 Met Station.xlsx",sheet = "Raw Data 2", skip = 0,col_names = T)

S3.3 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Canterbury/Soil Water Balance Files/Cant Site 3 SWB (V1).xlsx",sheet = "soil water balance", skip = 23,col_names = paste0("col",1:63)) 

S3.4 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Canterbury/Soil Water Balance Files/Cant Site 3 SWB (V1).xlsx",sheet = "DFM data", skip = 5,col_names = T)

S3.4.1 <- P_Data %>% filter(Site == 3) %>%  select(-c("Site"))

S3.5 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Canterbury/Cant Site 3 (McEvedy)/Results/Cant 3 Diary and Results.xlsx",sheet = "Soil Chemical", skip = 2,col_names = T)

S3.6 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Canterbury/Cant Site 3 (McEvedy)/Results/Cant 3 Diary and Results.xlsx",sheet = "Biomass Summary", skip = 0,col_names = T)

Site3.1 <-   Sum_x.1(S3.1)
Site3.2 <-   Sum_x.2(S3.2)
Site3.3 <-   Sum_x.3(S3.3)
Site3.4.1 <- Sum_x.4_Gen(S3.4)
Site3.4.2 <- Sum_x.4.1(Site3.4.1)
Site3.4.3 <- Sum_x.4.2(Site3.4.1)
Site3.4.4 <- Sum_x.4.3(Site3.4.1)
Site3.4.5 <- merge(Site3.4.4,S3.4.1, by = c("Date"), all = TRUE)
Site3.5.1 <- Sum_x.5(S3.5)
Site3.6 <- Sum_x.6(S3.6)

S3 <- Reduce(function(x, y) merge(x, y, all = TRUE), list(Site3.1,Site3.2, Site3.3,Site3.4.2, Site3.4.3, Site3.4.5, Site3.5.1, Site3.6))

write_xlsx(S3, "//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/FIF Data Packages/FIF Data Packages/Excel Data Files/Canterbury Site 3.xlsx")
  
```

### Site 4 Files (includes measured soil moisture data - currently being recorded)
```{r, echo=FALSE} 
S4.1 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Manawatu/Soil Water Balance Files/Manawatu Site 4 SWB (V1).xlsx",sheet = "Climate file", skip = 3,col_names = T)

S4.2 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Manawatu/Manawatu Site 1 (Clarke)/Diary and Results/TDR Data/TDR Data Levin.xlsx",sheet = "Raw Data", skip = 0,col_names = T)

S4.3 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Manawatu/Soil Water Balance Files/Manawatu Site 4 SWB (V1).xlsx",sheet = "soil water balance", skip = 23,col_names = paste0("col",1:58)) 

S4.4 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Manawatu/Soil Water Balance Files/Manawatu Site 4 SWB (V1).xlsx",sheet = "DFM data", skip = 5,col_names = T)

S4.4.1 <- P_Data %>% filter(Site == 4) %>%  select(-c("Site"))

S4.5 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Manawatu/Manawatu Site 1 (Clarke)/Diary and Results/Manawatu Site 1 Diary and Results.xlsx",sheet = "Soil Chemical", skip = 2,col_names = T)

S4.6 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Manawatu/Manawatu Site 1 (Clarke)/Diary and Results/Manawatu Site 1 Diary and Results.xlsx",sheet = "Biomass Summary", skip = 0,col_names = T)

Site4.1 <-   Sum_x.1(S4.1)
Site4.2 <-   Sum_x.2(S4.2)
Site4.3 <-   Sum_x.3(S4.3)
Site4.4.1 <- Sum_x.4_Gen(S4.4)
Site4.4.2 <- Sum_x.4.1(Site4.4.1)
Site4.4.3 <- Sum_x.4.2(Site4.4.1)
Site4.4.4 <- Sum_x.4.3(Site4.4.1)
Site4.4.5 <- merge(Site4.4.4,S4.4.1, by = c("Date"), all = TRUE)
Site4.5.1 <- Sum_x.5(S4.5)
Site4.6 <- Sum_x.6(S4.6)

S4 <- Reduce(function(x, y) merge(x, y, all = TRUE), list(Site4.1,Site4.2, Site4.3,Site4.4.2, Site4.4.3, Site4.4.5, Site4.5.1, Site4.6))

write_xlsx(S4, "//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/FIF Data Packages/FIF Data Packages/Excel Data Files/Manawatu Site 4.xlsx")
  
```

### Site 5 Files (No x.2 as no logging gear at this site)
```{r, echo=FALSE} 
S5.1 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Manawatu/Soil Water Balance Files/Manawatu Site 5 SWB (V1).xlsx",sheet = "Climate file", skip = 3,col_names = T)

S5.3 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Manawatu/Soil Water Balance Files/Manawatu Site 5 SWB (V1).xlsx",sheet = "soil water balance", skip = 23,col_names = paste0("col",1:63)) 

S5.4 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Manawatu/Soil Water Balance Files/Manawatu Site 5 SWB (V1).xlsx",sheet = "DFM data", skip = 5,col_names = T)

S5.4.1 <- P_Data %>% filter(Site == 5) %>%  select(-c("Site"))

S5.5 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Manawatu/Manawatu Site 2 (Dalrymple)/Diary and Results/Manawatu Site 2 Diary and Results.xlsx",sheet = "Soil Chemical", skip = 2,col_names = T)

S5.6 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Manawatu/Manawatu Site 2 (Dalrymple)/Diary and Results/Manawatu Site 2 Diary and Results.xlsx",sheet = "Biomass Summary", skip = 0,col_names = T)

Site5.1 <-   Sum_x.1(S5.1)
Site5.3 <-   Sum_x.3(S5.3)
Site5.4.1 <- Sum_x.4_Gen(S5.4)
Site5.4.2 <- Sum_x.4.1(Site5.4.1)
Site5.4.3 <- Sum_x.4.2(Site5.4.1)
Site5.4.4 <- Sum_x.4.3(Site5.4.1)
Site5.4.5 <- merge(Site5.4.4,S5.4.1, by = c("Date"), all = TRUE)
Site5.5.1 <- Sum_x.5(S5.5)
Site5.6 <- Sum_x.6(S5.6)

S5 <- Reduce(function(x, y) merge(x, y, all = TRUE), list(Site5.1,Site5.3,Site5.4.2, Site5.4.3, Site5.4.5, Site5.5.1, Site5.6))

write_xlsx(S5, "//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/FIF Data Packages/FIF Data Packages/Excel Data Files/Manawatu Site 5.xlsx")
  
```


### Site 6 Files (includes measured some soil moisture data - not currently being recorded)
```{r, echo=FALSE} 
S6.1 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Manawatu/Soil Water Balance Files/Manawatu Site 6 SWB (V1).xlsx",sheet = "Climate file", skip = 3,col_names = T)

S6.2 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Manawatu/Manawatu Site 3 (Wilcox)/Diary and Results/Ohakune SWC data.xlsx",sheet = "logger data", skip = 18,col_names = T)

S6.3 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Manawatu/Soil Water Balance Files/Manawatu Site 6 SWB (V1).xlsx",sheet = "soil water balance", skip = 23,col_names = paste0("col",1:63)) 

S6.4 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Manawatu/Soil Water Balance Files/Manawatu Site 6 SWB (V1).xlsx",sheet = "DFM data", skip = 5,col_names = T)

S6.4.1 <- P_Data %>% filter(Site == 6) %>%  select(-c("Site"))

S6.5 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Manawatu/Manawatu Site 3 (Wilcox)/Diary and Results/Manawatu Site 3 Diary and Results.xlsx",sheet = "Soil Chemical", skip = 2,col_names = T)

S6.6 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Manawatu/Manawatu Site 3 (Wilcox)/Diary and Results/Manawatu Site 3 Diary and Results.xlsx",sheet = "Biomass Summary", skip = 0,col_names = T)

Site6.1 <-   Sum_x.1(S6.1)
Site6.2 <-   Sum_x.2(S6.2)
Site6.3 <-   Sum_x.3(S6.3)
Site6.4.1 <- Sum_x.4_Gen(S6.4)
Site6.4.2 <- Sum_x.4.1(Site6.4.1)
Site6.4.3 <- Sum_x.4.2(Site6.4.1)
Site6.4.4 <- Sum_x.4.3(Site6.4.1)
Site6.4.5 <- merge(Site6.4.4,S6.4.1, by = c("Date"), all = TRUE)
Site6.5.1 <- Sum_x.5(S6.5)
Site6.6 <- Sum_x.6(S6.6)

S6 <- Reduce(function(x, y) merge(x, y, all = TRUE), list(Site6.1,Site6.2, Site6.3,Site6.4.2, Site6.4.3, Site6.4.5, Site6.5.1, Site6.6))

write_xlsx(S6, "//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/FIF Data Packages/FIF Data Packages/Excel Data Files/Manawatu Site 6.xlsx")
  
```

### Site 7 OLD Files (No x.2 as no logging gear at this site)
### Flooded Outliers denoted by xxx in Raw Data
```{r, echo=FALSE} 
S7.1 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/Soil Water Balance Files/HB Site 7 (OLD) SWB (V1).xlsx",sheet = "Climate file", skip = 3,col_names = T)

S7.3 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/Soil Water Balance Files/HB Site 7 (OLD) SWB (V1).xlsx",sheet = "soil water balance", skip = 23,col_names = paste0("col",1:63)) 

S7.4 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/Soil Water Balance Files/HB Site 7 (OLD) SWB (V1).xlsx",sheet = "DFM data", skip = 5,col_names = T)

S7.4.1 <- P_Data %>% filter(Site == 7) %>%  select(-c("Site"))

S7.5 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/HB Site 1 (Hugh Richie)/Diary and Results/HB Site 1 Diary and Results.xlsx",sheet = "Soil Chemical", skip = 2,col_names = T)

S7.6 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/HB Site 1 (Hugh Richie)/Diary and Results/HB Site 1 Diary and Results.xlsx",sheet = "Biomass Summary", skip = 0,col_names = T)

Site7.1 <-   Sum_x.1(S7.1)
Site7.3 <-   Sum_x.3(S7.3)
Site7.4.1 <- Sum_x.4_Gen(S7.4)
Site7.4.2 <- Sum_x.4.1(Site7.4.1)
Site7.4.3 <- Sum_x.4.2(Site7.4.1)
Site7.4.4 <- Sum_x.4.3(Site7.4.1)
Site7.4.5 <- merge(Site7.4.4,S7.4.1, by = c("Date"), all = TRUE)
Site7.5.1 <- Sum_x.5(S7.5)
Site7.6 <- Sum_x.6(S7.6)

S7 <- Reduce(function(x, y) merge(x, y, all = TRUE), list(Site7.1, Site7.3,Site7.4.2, Site7.4.3, Site7.4.5, Site7.5.1, Site7.6))

write_xlsx(S7, "//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/FIF Data Packages/FIF Data Packages/Excel Data Files/Hawke's Bay Site 7.xlsx")
  
```

### Site 7 NEW Files (No x.2 as no logging gear at this site)
### Flooded Outliers denoted by xxx in Raw Data
```{r, echo=FALSE} 
S7.1_NEW <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/Soil Water Balance Files/HB Site 7 (NEW) SWB (V1).xlsx",sheet = "Climate file", skip = 3,col_names = T)

S7.3_NEW <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/Soil Water Balance Files/HB Site 7 (NEW) SWB (V1).xlsx",sheet = "soil water balance", skip = 23,col_names = paste0("col",1:63)) 

S7.4_NEW <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/Soil Water Balance Files/HB Site 7 (NEW) SWB (V1).xlsx",sheet = "DFM data", skip = 5,col_names = T)

S7.4.1_NEW <- P_Data %>% filter(Site == 7.2) %>%  select(-c("Site"))

S7.5_NEW <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/HB Site 1.2 (Hugh Richie - NEW)/Diary and Results/HB Site 1.2 Diary and Results.xlsx",sheet = "Soil Chemical", skip = 2,col_names = T)

S7.6_NEW <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/HB Site 1.2 (Hugh Richie - NEW)/Diary and Results/HB Site 1.2 Diary and Results.xlsx",sheet = "Biomass Summary", skip = 0,col_names = T)

Site7.1_NEW <-   Sum_x.1(S7.1_NEW)
Site7.3_NEW <-   Sum_x.3(S7.3_NEW)
Site7.4.1_NEW <- Sum_x.4_Gen(S7.4_NEW)
Site7.4.2_NEW <- Sum_x.4.1(Site7.4.1_NEW)
Site7.4.3_NEW <- Sum_x.4.2(Site7.4.1_NEW)
Site7.4.4_NEW <- Sum_x.4.3(Site7.4.1_NEW)
Site7.4.5_NEW <- merge(Site7.4.4_NEW,S7.4.1_NEW, by = c("Date"), all = TRUE)
Site7.5.1_NEW <- Sum_x.5(S7.5_NEW)
Site7.6_NEW <- Sum_x.6(S7.6_NEW)

S7_NEW <- Reduce(function(x, y) merge(x, y, all = TRUE), list(Site7.1_NEW, Site7.3_NEW,Site7.4.2_NEW, Site7.4.3_NEW, Site7.4.5_NEW, Site7.5.1_NEW, Site7.6_NEW))

write_xlsx(S7_NEW, "//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/FIF Data Packages/FIF Data Packages/Excel Data Files/Hawke's Bay Site 7_NEW.xlsx")
  
```


### Site 8 OLD (includes measured soil moisture data BUT EXCLUDES ALL DRAINAGE DATA)
```{r, echo=FALSE} 
S8.1 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/Soil Water Balance Files/HB Site 8 (OLD) SWB (V1).xlsx",sheet = "Climate file", skip = 3,col_names = T)

S8.2 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/HB Site 2 (Mark Apatu)/Diary and Results/TDR/TDR Data Apatu (Hawke's Bay 2).xlsx",sheet = "Data 2", skip = 0,col_names = T)

S8.3 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/Soil Water Balance Files/HB Site 8 (OLD) SWB (V1).xlsx",sheet = "soil water balance", skip = 23,col_names = paste0("col",1:61)) 

S8.4 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/Soil Water Balance Files/HB Site 8 (OLD) SWB (V1).xlsx",sheet = "DFM data", skip = 5,col_names = T)


S8.5 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/HB Site 2 (Mark Apatu)/Diary and Results/HB Site 2 Diary and Results.xlsx",sheet = "Soil Chemical", skip = 2,col_names = T)

S8.6 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/HB Site 2 (Mark Apatu)/Diary and Results/HB Site 2 Diary and Results.xlsx",sheet = "Biomass Summary", skip = 0,col_names = T)

Site8.1 <-   Sum_x.1(S8.1)
Site8.2 <-   Sum_x.2(S8.2)
Site8.3 <-   Sum_x.3(S8.3)
Site8.5.1 <- Sum_x.5(S8.5)
Site8.6 <- Sum_x.6(S8.6)

S8_OLD <- Reduce(function(x, y) merge(x, y, all = TRUE), list(Site8.1, Site8.2, Site8.3,Site8.5.1, Site8.6))

write_xlsx(S8_OLD, "//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/FIF Data Packages/FIF Data Packages/Excel Data Files/Hawke's Bay Site 8.xlsx")
```


### Site 8 NEW (includes measured soil moisture data)
```{r, echo=FALSE} 
S8.1_NEW <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/Soil Water Balance Files/HB Site 8 (NEW) SWB (V1).xlsx",sheet = "Climate file", skip = 3,col_names = T)

S8.2_NEW <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/HB Site 2.2 (Mark Apatu - NEW)/Diary & Results/TDR/TDR Data Apatu (Hawke's Bay 2).xlsx",sheet = "Data 2", skip = 0,col_names = T)

S8.3_NEW <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/Soil Water Balance Files/HB Site 8 (NEW) SWB (V1).xlsx",sheet = "soil water balance", skip = 23,col_names = paste0("col",1:62)) 

S8.4_NEW <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/Soil Water Balance Files/HB Site 8 (NEW) SWB (V1).xlsx",sheet = "DFM data", skip = 5,col_names = T)

S8.4.1_NEW <- P_Data %>% filter(Site == 8.2) %>%  select(-c("Site"))

S8.5_NEW <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/HB Site 2.2 (Mark Apatu - NEW)/Diary & Results/HB Site 2.2 Diary and Results.xlsx",sheet = "Soil Chemical", skip = 2,col_names = T)

S8.6_NEW <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/HB Site 2.2 (Mark Apatu - NEW)/Diary & Results/HB Site 2.2 Diary and Results.xlsx",sheet = "Biomass Summary", skip = 0,col_names = T)

Site8.1_NEW <-   Sum_x.1(S8.1_NEW)
Site8.2_NEW <-   Sum_x.2(S8.2_NEW)
Site8.3_NEW <-   Sum_x.3(S8.3_NEW)
Site8.4.1_NEW <- Sum_x.4_Gen(S8.4_NEW)
Site8.4.2_NEW <- Sum_x.4.1(Site8.4.1_NEW)
Site8.4.3_NEW <- Sum_x.4.2(Site8.4.1_NEW)
Site8.4.4_NEW <- Sum_x.4.3(Site8.4.1_NEW)
Site8.4.5_NEW <- merge(Site8.4.4_NEW,S8.4.1_NEW, by = c("Date"), all = TRUE)
Site8.5.1_NEW <- Sum_x.5(S8.5_NEW)
Site8.6_NEW <- Sum_x.6(S8.6_NEW)

S8_NEW <- Reduce(function(x, y) merge(x, y, all = TRUE), list(Site8.1_NEW,Site8.2_NEW, Site8.3_NEW,Site8.4.2_NEW, Site8.4.3_NEW, Site8.4.5_NEW, Site8.5.1_NEW, Site8.6_NEW))

write_xlsx(S8_NEW, "//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/FIF Data Packages/FIF Data Packages/Excel Data Files/Hawke's Bay Site 8_NEW.xlsx")
```




### Site 9 Files (No x.2 as no logging gear at this site)
```{r, echo=FALSE} 
S9.1 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/Soil Water Balance Files/HB Site 9 SWB (V1).xlsx",sheet = "Climate file", skip = 3,col_names = T)

S9.3 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/Soil Water Balance Files/HB Site 9 SWB (V1).xlsx",sheet = "soil water balance", skip = 23,col_names = paste0("col",1:63)) 

S9.4 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/Soil Water Balance Files/HB Site 9 SWB (V1).xlsx",sheet = "DFM data", skip = 5,col_names = T)

S9.4.1 <- P_Data %>% filter(Site == 9) %>%  select(-c("Site"))

S9.5 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/HB Site 3 (Richard Dakins)/Diary and Results/HB Site 3 Diary and Results.xlsx",sheet = "Soil Chemical", skip = 2,col_names = T)

S9.6 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Hawkes Bay/HB Site 3 (Richard Dakins)/Diary and Results/HB Site 3 Diary and Results.xlsx",sheet = "Biomass Summary", skip = 0,col_names = T)

Site9.1 <-   Sum_x.1(S9.1)
Site9.3 <-   Sum_x.3(S9.3)
Site9.4.1 <- Sum_x.4_S9(S9.4)
Site9.4.2 <- Sum_x.4.1(Site9.4.1)
Site9.4.3 <- Sum_x.4.2(Site9.4.1)
Site9.4.4 <- Sum_x.4.3(Site9.4.1)
Site9.4.5 <- merge(Site9.4.4,S9.4.1, by = c("Date"), all = TRUE)
Site9.6 <- Sum_x.6(S9.6)

S9 <- Reduce(function(x, y) merge(x, y, all = TRUE), list(Site9.1, Site9.3,Site9.4.2, Site9.4.3, Site9.4.5, Site9.6))

write_xlsx(S9, "//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/FIF Data Packages/FIF Data Packages/Excel Data Files/Hawke's Bay Site 9.xlsx")
  
```


### Site 10 Files (includes measured soil moisture data)
```{r, echo=FALSE} 
S10.1 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Northern/Soil Water Balance Files/Northern Site 10 SWB (V1).xlsx",sheet = "Climate file", skip = 3,col_names = T)

S10.2 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Northern/Northern Site 1 (Balle)/TDR/TDR Data - Balle (Northern 1).xlsx",sheet = "Raw Data", skip = 0,col_names = T)

S10.3 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Northern/Soil Water Balance Files/Northern Site 10 SWB (V1).xlsx",sheet = "soil water balance", skip = 23,col_names = paste0("col",1:63)) 

S10.4 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Northern/Soil Water Balance Files/Northern Site 10 SWB (V1).xlsx",sheet = "DFM data", skip = 5,col_names = T)

S10.4.1 <- P_Data %>% filter(Site == 10) %>%  select(-c("Site"))

S10.5 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Northern/Northern Site 1 (Balle)/Diary and Results/Northern Site 1 Diary and Results.xlsx",sheet = "Soil Chemical", skip = 2,col_names = T)

S10.6 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Northern/Northern Site 1 (Balle)/Diary and Results/Northern Site 1 Diary and Results.xlsx",sheet = "Biomass Summary", skip = 0,col_names = T)


Site10.1 <-   Sum_x.1(S10.1)
Site10.2 <-   Sum_x.2(S10.2)
Site10.3 <-   Sum_x.3(S10.3)
Site10.4.1 <- Sum_x.4_S10(S10.4)
Site10.4.2 <- Sum_x.4.1(Site10.4.1)
Site10.4.3 <- Sum_x.4.2(Site10.4.1)
Site10.4.4 <- Sum_x.4.3(Site10.4.1)
Site10.4.5 <- merge(Site10.4.4,S10.4.1, by = c("Date"), all = TRUE)
Site10.5.1 <- Sum_x.5(S10.5)

S10 <- Reduce(function(x, y) merge(x, y, all = TRUE), list(Site10.1, Site10.2, Site10.3,Site10.4.2, Site10.4.3, Site10.4.5, Site10.5.1))

write_xlsx(S10, "//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/FIF Data Packages/FIF Data Packages/Excel Data Files/Northern Site 10.xlsx")
  
```


### Site 11 Files (No x.2 as no logging gear at this site)
```{r, echo=FALSE} 
S11.1 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Northern/Soil Water Balance Files/Northern Site 11 SWB (V1).xlsx",sheet = "Climate file", skip = 3,col_names = T)

S11.3 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Northern/Soil Water Balance Files/Northern Site 11 SWB (V1).xlsx",sheet = "soil water balance", skip = 23,col_names = paste0("col",1:64))  

S11.4 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Northern/Soil Water Balance Files/Northern Site 11 SWB (V1).xlsx",sheet = "DFM data", skip = 5,col_names = T)

S11.4.1 <- P_Data %>% filter(Site == 11) %>%  select(-c("Site"))

S11.5 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Northern/Northern Site 2 (Jivan)/Diary and Results/Northern Site 2 Diary and Results.xlsx",sheet = "Soil Chemical", skip = 2,col_names = T)

S11.6 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Northern/Northern Site 2 (Jivan)/Diary and Results/Northern Site 2 Diary and Results.xlsx",sheet = "Biomass summary", skip = 0,col_names = T)

Site11.1 <-   Sum_x.1(S11.1)
Site11.3 <-   Sum_x.3(S11.3)
Site11.4.1 <- Sum_x.4_S11(S11.4)
Site11.4.2 <- Sum_x.4.1(Site11.4.1)
Site11.4.3 <- Sum_x.4.2(Site11.4.1)
Site11.4.4 <- Sum_x.4.3(Site11.4.1)
Site11.4.5 <- merge(Site11.4.4,S11.4.1, by = c("Date"), all = TRUE)
Site11.5.1 <- Sum_x.5(S11.5)
Site11.6 <- Sum_x.6(S11.6)

S11 <- Reduce(function(x, y) merge(x, y, all = TRUE), list(Site11.1,Site11.3,Site11.4.2, Site11.4.3, Site11.4.5, Site11.5.1, Site11.6))

write_xlsx(S11, "//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/FIF Data Packages/FIF Data Packages/Excel Data Files/Northern Site 11.xlsx")
  
```

### Site 12 Files (No x.2 as no logging gear at this site)
```{r, echo=FALSE} 
S12.1 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Northern/Soil Water Balance Files/Northern Site 12 SWB (V1).xlsx",sheet = "Climate file", skip = 3,col_names = T)

S12.3 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Northern/Soil Water Balance Files/Northern Site 12 SWB (V1).xlsx",sheet = "soil water balance", skip = 23,col_names = paste0("col",1:64))  

S12.4 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Northern/Soil Water Balance Files/Northern Site 12 SWB (V1).xlsx",sheet = "DFM data", skip = 5,col_names = T)

S12.4.1 <- P_Data %>% filter(Site == 12) %>%  select(-c("Site"))

S12.5 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Northern/Northern Site 3 (Masters)/Diary and Results/Northern Site 3 Diary and Results.xlsx",sheet = "Soil Chemical", skip = 2,col_names = T)

S12.6 <- read_excel("//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/Sites/Northern/Northern Site 3 (Masters)/Diary and Results/Northern Site 3 Diary and Results.xlsx",sheet = "Biomass Summary", skip = 0,col_names = T)

Site12.1 <-   Sum_x.1(S12.1)
Site12.3 <-   Sum_x.3(S12.3)
Site12.4.1 <- Sum_x.4_S12(S12.4)
Site12.4.2 <- Sum_x.4.1(Site12.4.1)
Site12.4.3 <- Sum_x.4.2(Site12.4.1)
Site12.4.4 <- Sum_x.4.3(Site12.4.1)
Site12.4.5 <- merge(Site12.4.4,S12.4.1, by = c("Date"), all = TRUE)
Site12.5.1 <- Sum_x.5(S12.5)
Site12.6 <- Sum_x.6(S12.6)

S12 <- Reduce(function(x, y) merge(x, y, all = TRUE), list(Site12.1,Site12.3,Site12.4.2, Site12.4.3, Site12.4.5, Site12.5.1, Site12.6))

write_xlsx(S12, "//Hawdfs41/data/Common/EXPTS/Commercial/F A R/SFF Fluxmeter/Sites and Results/FIF Data Packages/FIF Data Packages/Excel Data Files/Northern Site 12.xlsx")
  
```




