---
title: "get to the bottom of the data issue"
output: html_document
---

# Issue

Reported drainage does not match FIF data package 

Some notes: 

1. P data is genereted by R and directly used by the report   
2. N and D data were compiled in excel files and used for report.  
3. N and D data were also processed in R to generate the FIF data package. 

Assumptions of the issue: 
1. Excel files have pivot table data compiled by hand and clear thinking 
2. R process might stuff up the filtering process. 

Action:

1. read the data from pivot table in the swb 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(data.table)
library(magrittr)
# CONSTANT
sheetname = "Yearly Summary"
l <- vector("list", length = 9)
names(l) <- paste0("site", c(3, 5:12))
```

```{r}
region <- "Cant"
checknames <- grep(region, readRDS("SWBfilenames.rds"),
                   value = TRUE)
```

```{r}
DT <- read_excel(checknames[3], sheet =  "DFM data pivot", skip = 18, 
                 .name_repair = "universal") %>% 
  as.data.table()
DT_sub <- DT[!is.na(YEAR), .(YEAR, Drainage.model..mm.,Drainage.data..mm.)]
sum <- DT_sub[, .(Drainage.model..mm. = sum(Drainage.model..mm., na.rm = TRUE),
                  Drainage.data..mm. = sum(Drainage.data..mm., na.rm = TRUE)),
              by = .(YEAR)]


l$site3 <- sum
```

```{r}
region <- "Manawatu"
checknames <- grep(region, readRDS("SWBfilenames.rds"),
                   value = TRUE)
```

```{r}
DT <- read_excel(checknames[1], sheet =  "DFM data pivot", skip = 18, 
                 .name_repair = "universal") %>% 
  as.data.table()
DT_sub <- DT[!is.na(YEAR), .(YEAR, Drainage.model..mm.,Drainage.data..mm.)]
sum <- DT_sub[, .(Drainage.model..mm. = sum(Drainage.model..mm., na.rm = TRUE),
                  Drainage.data..mm. = sum(Drainage.data..mm., na.rm = TRUE)),
              by = .(YEAR)]

l$site5 <- sum
DT <- read_excel(checknames[2], sheet =  "DFM data pivot", skip = 18, 
                 .name_repair = "universal") %>% 
  as.data.table()
DT_sub <- DT[!is.na(YEAR), .(YEAR, Drainage.model..mm.,Drainage.data..mm.)]
sum <- DT_sub[, .(Drainage.model..mm. = sum(Drainage.model..mm., na.rm = TRUE),
                  Drainage.data..mm. = sum(Drainage.data..mm., na.rm = TRUE)),
              by = .(YEAR)]


l$site6 <- sum
```

```{r}
region <- "Northern"
checknames <- grep(region, readRDS("SWBfilenames.rds"),
                   value = TRUE)
```

```{r}
DT <- read_excel(checknames[1],  sheet =  "DFM data pivot", skip = 18, 
                 .name_repair = "universal") %>% 
  as.data.table()
DT_sub <- DT[!is.na(YEAR), .(YEAR, Drainage.model..mm.,Drainage.data..mm.)]
sum <- DT_sub[, .(Drainage.model..mm. = sum(Drainage.model..mm., na.rm = TRUE),
                  Drainage.data..mm. = sum(Drainage.data..mm., na.rm = TRUE)),
              by = .(YEAR)]

l$site10 <- sum

## Site 11 PROBLEM------
DT <- read_excel(checknames[2], sheet =  "DFM data pivot", skip = 18, 
                 .name_repair = "universal") %>% 
  as.data.table()
DT_sub <- DT[!is.na(YEAR), .(YEAR, Drainage.model..mm.,Drainage.data..mm., 
                             Drainage.data.INPUT._.mm.)]
sum <- DT_sub[, .(Drainage.model..mm. = sum(Drainage.model..mm., na.rm = TRUE),
                  Drainage.data..mm. = sum(Drainage.data..mm., na.rm = TRUE),
                  Drainage.data.INPUT._.mm. = sum(Drainage.data.INPUT._.mm., 
                                                  na.rm = TRUE)),
              by = .(YEAR)]

l$site11 <- sum

# Site 12 
# Year 4 is ok to leave it 
# Year 6 used modelled data 
DT <- read_excel(checknames[3], sheet = "DFM data pivot", skip = 18,
                 .name_repair = "universal") %>% 
  as.data.table()
DT_sub <- DT[!is.na(YEAR), .(YEAR, Drainage.model..mm.,Drainage.data..mm., 
                             Drainage.INPUT..mm.)]
sum <- DT_sub[, .(Drainage.model..mm. = sum(Drainage.model..mm., na.rm = TRUE),
                  Drainage.data..mm. = sum(Drainage.data..mm., na.rm = TRUE),
                  Drainage.data.INPUT._.mm. = sum(Drainage.INPUT..mm., 
                                                  na.rm = TRUE)),
              by = .(YEAR)]

l$site12<- sum
```


# HB

```{r}
region <- "HB"
checknames <- grep(region, readRDS("SWBfilenames.rds"),
                   value = TRUE)
```

```{r}
swb_l <- lapply(checknames[1:2], function(x){
  swb <- read_excel(x,
                    sheet =  "DFM data pivot", skip = 18,
                    .name_repair = "universal") %>% 
    as.data.table()
  DT_sub <- swb[!is.na(YEAR), .(YEAR, Drainage.model..mm.,Drainage.data..mm.)]
  sum <- DT_sub[, .(Drainage.model..mm. = sum(Drainage.model..mm., na.rm = TRUE),
                    Drainage.data..mm. = sum(Drainage.data..mm., na.rm = TRUE)),
                by = .(YEAR)]

  })
swb_sub <- rbindlist(swb_l)[order(YEAR)]


l$site7 <- swb_sub

swb_l <- lapply(checknames[3:4], function(x){
  swb <- read_excel(x,
                    sheet =  "DFM data pivot", skip = 18,
                    .name_repair = "universal") %>% 
    as.data.table()
  DT_sub <- swb[!is.na(YEAR), .(YEAR, Drainage.model..mm.,Drainage.data..mm.)]
  sum <- DT_sub[, .(Drainage.model..mm. = sum(Drainage.model..mm., na.rm = TRUE),
                    Drainage.data..mm. = sum(Drainage.data..mm., na.rm = TRUE)),
                by = .(YEAR)]

  })
swb_sub <- rbindlist(swb_l)[order(YEAR)]


l$site8 <- swb_sub

DT <- read_excel(checknames[5], sheet =  "DFM data pivot", skip = 16, 
                 .name_repair = "universal") %>% 
  as.data.table()
DT_sub <- DT[!is.na(YEAR), .(YEAR, Drainage.model..mm.,Drainage.data..mm.)]
sum <- DT_sub[, .(Drainage.model..mm. = sum(Drainage.model..mm., na.rm = TRUE),
                  Drainage.data..mm. = sum(Drainage.data..mm., na.rm = TRUE)),
              by = .(YEAR)]


l$site9 <- sum
```

```{r}
output <- rbindlist(l, fill = TRUE, use.names = TRUE, idcol = "Site")

fwrite(x = output, file = "output.csv")
```
